The Shape Matching Element Method: Direct Animation of Curved Surface Models

### 2021-01-27 paper/sections/conclusion.tex
updated results

\section{Future Work and Conclusions}
\dave{mention we focus on animation ... lots of work to validate this for engineering applications}
We have presented the Shape Matching Element Method (SEM), the first completely meshless approach to direct simulation of NURBS models.
Our approach is unique in its ability to infer volumetric shape from surface only models,
including ones with intersecting geometry, between parts and other defects common to non-engineering models.
Our method allows simulation of such input directly, with a variety of contitutive models and time integration schemes
and is compatibale with standard methods for collision resolution. 
We believe that SEM is a significant improvement over standard physics-based animation pipelines for NURBS models. 
As evidence of the efficacy of our approach, the authors submit that many of the examples in this paper were constructed ourselves
(since the standard graphics menagerie is not available as NURBS models). 
Modelling, cleaning, meshing and simulating would've been a burdensome experience without SEM's
ability to leap directly from (often hastily) constructed models to physics-based animations.

>>>>

\section{Future Work and Conclusions}
\dave{mention we focus on animation ... lots of work to validate this for engineering applications}
We have presented the Shape Matching Element Method (SEM), the first completely meshless approach to direct simulation of NURBS models.
Our approach is unique in its ability to infer volumetric shape from surface only models,
including ones with intersecting geometry between parts and other defects common to non-engineering models.
Our method allows simulation of such input directly with a variety of constitutive models and time integration schemes,
and is compatible with standard methods for collision resolution. 
We believe that SEM is a significant improvement over standard physics-based animation pipelines for NURBS models. 
As evidence of the efficacy of our approach, the authors submit that many of the examples in this paper were constructed ourselves
(since the standard graphics menagerie is not available as NURBS models). 
Modelling, cleaning, meshing and simulating would've been a burdensome experience without SEM's
ability to leap directly from (often hastily) constructed models to physics-based animations.

### 2021-01-27 paper/sections/intro.tex
updated results

We present the first truly meshless (no volumetric discretization generated) algorithm for direct, nonlinear elastodynamic simulation of NURBs models. 
Our nonlinear elastodynamic simulation scheme requires only a boundary description of the object (we do not strictly require a solid model) and
approriate physical parameters.  
Because we explicitly use the NURBS boundary representation in the simulation it is straightforward to handle
Dirichilet and Neumann boundary conditions and to apply contact resolution. 
Crucially because we broadly target animation not necessarily simulation for engineering or manufacturing, we don't require that models
satisfy the rigourous geometric requirements common for these applications

>>>>

We present the first truly meshless (no volumetric discretization generated) algorithm for direct, nonlinear elastodynamic simulation of NURBs models. 
Our nonlinear elastodynamic simulation scheme requires only a boundary description of the object (we do not strictly require a solid model) and
approriate physical parameters.  
Because we explicitly use the NURBS boundary representation in the simulation, it is straightforward to handle
Dirichlet and Neumann boundary conditions and to apply contact resolution. 
Crucially because we broadly target animation not necessarily simulation for engineering or manufacturing, we don't require that models
satisfy the rigourous geometric requirements common for these applications

### 2021-01-27 paper/sections/results.tex
Added grumpy figure, not super happy with how it turned out
figure settings
fixed typos and added an empty figure
fixed typos
updated results

@@

\dave{rendering we convert to triangle meshes, just didn't have a good path tracer lying around}

\begin{table*}[h]
  \caption{Performance of the Shape Matching Element Method on all Examples. \dave{need table that also reports material params/constitutive model or add it here}}
  \label{tbl:perf}
  \begin{center}
  \begin{tabular}{l c c c c c c c c}
   \textbf{Example} & \textbf{CPU} & $|\vc{q}|$ &  \textbf{Sample Model} & \textbf{Quadrature} & \textbf{Weights} & \textbf{Build $\Pi$} & \textbf{Time Step} \\
   \hline 
   \rowcolor[HTML]{DAE8FC} 
   \textbf{Cantilever}  & ? & ? & ? & ? & ? & ? & ? & ? \\
   \textbf{Rocket}      & ? & ? & ? & ? & ? & ? & ? & ? \\
   \hline
  \end{tabular}
  \end{center}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{figures/patch_test.pdf}
  \caption{2D examples (left) rigidly transform boundary and show that solving the static problem gives us rigid motion on the interior (right) isotropically scale boundary and show solving static problem gives us constant strain on the interior}
  \label{fig:patchtest}
\end{figure}

Next we check the convergence of SEM with respect to linear, tetrahedral finite elements. \reffig{convergence} we compare identical cantileavered beams, simulated using 
a Neohookean constitutive model (Young's Modulus \dave{??}, Poisson's Ratio \dave{??}) and implicit time integration with a timestep of $0.01$s. 
We use SEM with quadratic polynomials for this test and observe that our SEM simulation, made of 6 independent NURBS patches show's good agreement with FEM.
\begin{figure}
  \includegraphics[width=\columnwidth]{example-image-a}
  \caption{(left) high res FEM cantileavered bar (right) several simulations using more and more surface patches plus center of mass. Need to show beam is just  unattached patches}
  \label{fig:convergence}
\end{figure}

We also demonstrate that our raycasting weights computation creates shape-aware output. Figure~\reffig{independence} shows that manipulating
parts that are nearby, but separate  behave in an appropriately independent fashion. 
\begin{figure}
  \includegraphics[width=\columnwidth]{example-image-a}
  \caption{X shape and show arms of X move independently}
  \label{fig:independence}
\end{figure}

% relaxed modeling  constraints
Here we demonstrate SEM's ability to work with poor models. \reffig{badmodels} shows simulations of two jelly coffee mugs. 
The top row shows the result of a careless modeler who has deeply embedded the handle of the mug in the body in order to attach it, creating a large area of overlap.
The bottom models has neglible overlap. 
In both cases SEM produces a plausible physically-based animation, without requiring additional model clean-up.
\begin{figure}
  \includegraphics[width=\columnwidth]{figures/mug_overlap}
  \caption{Coffee mug with overlapping handle (top) row of models with increasing overlap (middle) single weight image showing behaviour in the overlapping region, (bottom) simulation result for each one}
  \label{fig:badmodels}
\end{figure}

%different material parameters / material models 
We derive the equations of motion for SEM using a general elastic potential and so SEM supports arbitrary constitutive models. \reffig{materials} shows a 
rocket ship simulated with both high stiffness and low stiffness materials. 
\begin{figure*}
  \includegraphics[width=\textwidth]{figures/rocket.pdf}
  \caption{Big image simulating the rocket with all different combinations of things}
  \label{fig:materials}
\end{figure*}

%multiple materials
SEM also supports objects made up of multiple materials, as the simulation of this tire~(\reffig{tire}) illustrates.
\begin{figure}
  \includegraphics[width=\columnwidth]{figures/tire}
  \caption{Tire to show heterogenous materials}
  \label{fig:tire}
\end{figure}

%different surface reps
Though we focus on NURBS surface representations, they only NURBS specific construction in the SEM method is the Jacobian\dave{ref}.
Many other boundary representations admit a linear representation and are thus directly consumable by our method.
\reffig{subd} shows an example of applying our SEM method to a subdivision model by making such a modification.
\begin{figure}
  \includegraphics[width=\columnwidth]{example-image-a}
  \caption{show subd simulation if we have it. If it works really well we'll just mix subds and nurbs throughout the paper. }
  \label{fig:subd}
\end{figure}

%editing example
We show that the output of the SEM simulation is itself edible in a NURBS modelling program~(\reffig{edit}).
\begin{figure}
  \includegraphics[width=\columnwidth]{example-image-a}
  \caption{show input to simulation, show output then show output loaded in rhino/fusion 360 }
  \label{fig:edit}
\end{figure}

%show stoppers
Finally we show the ability of SEM to handle complex simulations involving deformation, contact and friction~(\reffig{staypuft} and \reffig{f1})).
\begin{figure*}[htp]
  \includegraphics[width=\textwidth,height=3in]{example-image-a}
  \caption{sequence of frames from staypuft simulation}
  \label{fig:staypuft}
\end{figure*}

>>>>

\begin{figure*}
  \includegraphics[width=\textwidth]{figures/chicken.pdf}
  \caption{Simulation of a chicken model with gaps between surfaces}
  \label{fig:chicken}
\end{figure*}

@@

For raycasting operations and rendering, we triangulate the NURBS surfaces, which only represents an implementation simplification. Our algorithm is not dependent on triangulating the boundary, and an ideally one would use a path tracer.

\ty{Would be nice to mention TNURBS, which would give us a good reason to include the wrench (which i really wanna do). I doubt we have time to do a 3 point bending test, but a simple elastic wrench simulation would be easy to cook up}
For handling trimmed NURBS surfaces, we augment our sampling of the surfaces by using raycasting integration in 2D. Trimmed NURBS may be defined by a boundary curve in the parametric space, so we raycast to find intersection intervals in the UV space on which quadrature points are generated. For rendering Trimmed NURBS, we discretize the the boundary curve as a polyline and use triangle ~\ty{cite} to form a boundary conforming triangulation. The vertices of this triangulation serve as fixed set of high resolution UV samples for constructing a render mesh.

\begin{table*}[h]
  \caption{Performance of the Shape Matching Element Method on all Examples. \dave{need table that also reports material params/constitutive model or add it here}}
  \label{tbl:perf}
  \begin{center}
  \begin{tabular}{l c c c c c c c c}
   \textbf{Example} & \textbf{CPU} & $|\vc{q}|$ &  \textbf{Sample Model} & \textbf{Quadrature} & \textbf{Weights} & \textbf{Build $\Pi$} & \textbf{Time Step} \\
   \hline 
   \rowcolor[HTML]{DAE8FC} 
   \textbf{Cantilever}      & ? & ? & ? & ? & ? & ? & ? & ? \\
   \textbf{Coffee mug}      & ? & ? & ? & ? & ? & ? & ? & ? \\
   \textbf{Rocket}          & ? & 648 & ? & ? & ? & ? & ? & ? \\
   \textbf{Castle}          & ? & ? & ? & ? & ? & ? & ? & ? \\
   \textbf{Chicken}         & ? & ? & ? & ? & ? & ? & ? & ? \\
   \textbf{Starship}        & ? & ? & ? & ? & ? & ? & ? & ? \\
   \textbf{Tire}            & ? & ? & ? & ? & ? & ? & ? & ? \\
   \hline
  \end{tabular}
  \end{center}

@@

\begin{figure}[h]
  \includegraphics[width=\columnwidth]{figures/patch_test.pdf}
  \caption{2D examples (left) undeformed model defined by four surface elements on the boundary (right) applying affine transformations to the boundary and show that solving the static problem gives rigid motion for rotation and constant strain for shearing and stretching}
  \label{fig:patchtest}
\end{figure}

Next we check the convergence of SEM with respect to linear, tetrahedral finite elements. \reffig{convergence} we compare identical cantilevered beams, simulated using 
a Neohookean constitutive model (Young's Modulus $0.001$ GPa, Poisson's Ratio 0.45) and implicit time integration with a timestep of $0.01$s. 
We use SEM with quadratic polynomials for this test and observe that our SEM simulation, made of 24 independent NURBS patches shows good agreement with FEM. Each subdivision of the NURBS beam enables more complicated kinematics, but very few surface elements are needed to produce compelling results.

\begin{figure}[h]
  \includegraphics[width=\columnwidth]{figures/beams.pdf}
  \caption{(left) high res FEM cantilevered bar (right) several simulations using more and more surface.}
  \label{fig:convergence}
\end{figure}

We also demonstrate that our raycasting weight computation creates shape-aware output. Figure~\reffig{independence} shows that manipulating
parts that are nearby but separate will behave in an appropriately independent fashion. 
\begin{figure}[h]
  \includegraphics[width=\columnwidth]{figures/independent_movement}
  \caption{X shape and show arms of X move independently}
  \label{fig:independence}
\end{figure}

% relaxed modelling  constraints
Here we demonstrate SEM's ability to work with poor models. \reffig{badmodels} shows simulations of two jelly coffee mugs. 
The top row shows a model with negligible overlap, whereas the bottom row shows the result of a careless modeller who has deeply embedded the handle of the mug in the body in order to attach it, creating a large area of overlap.
In both cases SEM produces a plausible physically-based animation, without requiring additional model clean-up.
\begin{figure}[h]
  \includegraphics[width=\columnwidth]{figures/mug_overlap}
  \caption{Coffee mug with overlapping handle (top) row of models with increasing overlap (middle) single weight image showing behaviour in the overlapping region, (bottom) simulation result for each one}
  \label{fig:badmodels}
\end{figure}
Similarly, in \reffig{chicken} we show a simulation with gaps between surfaces. Despite the lack of explicit connectivity, the blending weights have the effect of implicitly enforcing connections at these seams.

%different material parameters / material models 
We derive the equations of motion for SEM using a general elastic potential and so SEM supports arbitrary constitutive models. \reffig{materials} shows a 
rocket ship simulated with both high stiffness and low stiffness materials. 
\begin{figure*}[htp]
  \includegraphics[width=\textwidth]{figures/rocket.pdf}
  \caption{Big image simulating the rocket with all different combinations of things}
  \label{fig:rocket}
\end{figure*}

%multiple materials
SEM also supports objects made up of multiple materials, as the simulation of this tire~(\reffig{tire}) illustrates.
\begin{figure}[h]
  \includegraphics[width=\columnwidth]{figures/tire}
  \caption{Tire to show heterogenous materials}
  \label{fig:tire}
\end{figure}

%different surface reps
Though we focus on NURBS surface representations, the only NURBS specific construction in the SEM method is the Jacobian\dave{ref}.
Many other boundary representations admit a linear representation and are thus directly consumable by our method.
\reffig{subd} shows an example of applying our SEM method to a subdivision model by making such a modification.
\begin{figure}[h]
  \includegraphics[width=\columnwidth]{example-image-a}
  \caption{show subd simulation if we have it. If it works really well we'll just mix subds and nurbs throughout the paper. }
  \label{fig:subd}
\end{figure}

% different time integration scheme
\begin{figure}[h]
  \includegraphics[width=\columnwidth]{example-image-a}
  \caption{show mug simulation using newton's method, linearly implicit Euler (and maybe RK4). }
  \label{fig:time_integration}
\end{figure}

%editing example
We show that the output of the SEM simulation is itself edible in a NURBS modelling program~(\reffig{edit}).
\begin{figure}[h]
  \includegraphics[width=\columnwidth]{example-image-a}
  \caption{show input to simulation, show output then show output loaded in rhino/fusion 360 }
  \label{fig:edit}
\end{figure}

%show stoppers
Finally we show the ability of SEM to handle complex simulations involving deformation, contact and friction~(\reffig{staypuft} and \reffig{f1}).
\begin{figure*}[htp]
  \includegraphics[width=\textwidth,height=3in]{example-image-a}
  \caption{sequence of frames from staypuft simulation}
  \label{fig:staypuft}
\end{figure*}
